\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{\articletitle}

### 2015-04-07 paper/paper.tex
paper updates
Merge branch 'devnew' of C:\Users\Jeroen\Projects\PycharmProjects\Graph-Isomorphism with conflicts.

\section{Table with computation times}
\begin{tabular}{c|c|c}
Graph & Computation time (without preprocessing) & Computation time (with preprocessing) \\
\hline
cographs1 & 146.8098 sec & 0.0171 sec \\
hugecographs & >30 min & 662.5381 sec \\
cycles175 & 69.8579 & 70.8041 sec \\
bigtrees3 & -1 & -1\\
cubes6 & -1 & -1\\
products72 & -1 & -1\\
torus72 & -1 & -1\\

@@

>>>>

\section{Table with computation times}
\begin{tabular}{c|c|c}
Graph & Computation time (without preprocessing) & Computation time (with preprocessing) \\
\hline
cographs1 & 146.8098 sec & 0.0171 sec \\
hugecographs & >30 min & 662.5381 sec \\
cycles175 & 69.8579 & 70.8041 sec \\
bigtrees3 & 8.2151 & 2.5008\\
cubes6 & -1 & -1\\
products72 & -1 & -1\\
torus72 & -1 & -1\\

@@

\section{Table with computation times}
\begin{tabular}{c|c|c|c}
Graph & Computation time (without preprocessing) & Computation time (with preprocessing) & Preprocessing time \\
\hline
cographs1 & 146.8098 sec & 0.0171 sec & 0.0056 sec \\
hugecographs & >30 min & 662.5381 sec & 0.0316 sec \\
cycles175 & 69.8579 sec & 70.8041 sec & 0.0215 sec\\
bigtrees3 & 8.2724 sec & 2.8264 & 0.0499 sec\\
cubes6 & -1 & -1\\
products72 & -1 & -1\\
torus72 & -1 & -1\\
\end{tabular}
